---
title: "MAFtools_WXS"
output: html_document
date: "2022-12-09"
---

```{r}
library(maftools)
```

1. VCFs to MAFs  (vcf2maf) -- Brandon gave me these 
2. Keep MAfs in one folder 
3. Merge MAfs to a single MAF (merge_mafs)
4. Do the standard analysis 
5. Can only do comparisons of 2 time points at a time with mafCompare. I want the beginning and end time point 

This is going to start a general trend of what is happening across all samples as well as some surface level info.
This is ONLY WXS

```{r}
mafs <- list.files("~/Desktop/ovarian_cancer_somatic_variants_mafs/WXS/", full.names= TRUE)
anoikis_maf <- merge_mafs(mafs)
```

```{r}
#Shows sample summary.
save_mutation_type <- getSampleSummary(anoikis_maf)
write.csv(save_mutation_type, "~/Desktop/wxs_anoikis_ov90_mutations.csv")
save_mutation_type
```


```{r}
#Shows gene summary.
getGeneSummary(anoikis_maf)
```


```{r}
#Shows all fields in MAF
getFields(anoikis_maf)
```

```{r}
plotmafSummary(maf = anoikis_maf, rmOutlier = TRUE, addStat = 'median', dashboard = TRUE, titvRaw = FALSE)
```

```{r}
laml.titv = titv(maf = anoikis_maf, plot = FALSE, useSyn = TRUE)
#plot titv summary
plotTiTv(res = laml.titv)
```

```{r}
laml.sig = oncodrive(maf = anoikis_maf, AACol = 'HGVSp_Short', minMut = 5, pvalMethod = 'zscore')
```

```{r}
plotOncodrive(res = laml.sig, fdrCutOff = 0.1, useFraction = TRUE, labelSize = 0.5)
```


Changed the columns to include time points manually, so we are going to export the CSV back in and then make a graph
```{r}
anoikis_wxs <- read.csv("~/Desktop/wxs_anoikis_ov90_mutations.csv")
```

```{r}
library(tidyr)
anoikis_wxs_2 <- anoikis_wxs %>%
  pivot_longer(cols= c(Frame_Shift_Del, Frame_Shift_Ins, In_Frame_Del,In_Frame_Ins,Missense_Mutation, Nonsense_Mutation, Nonstop_Mutation, Splice_Site, Translation_Start_Site), names_to = "Mutation", values_to= "counts")
```


```{r}
library(ggplot2)
```

```{r}
ggplot(anoikis_wxs_2, aes(x = Tumor_Sample_Barcode, y = counts, color= Mutation)) + geom_point() 
```

